Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-29 paper.tex
Revise abstract

\maketitle
\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
  Probably "Analytical model for  porous silicon structures with 1D
  gradient refractive index)}
\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
\begin{abstract}
  We propose a simple setup with which that the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.
\notaV{ABSTRACT :  Surfaces with the gradient in the refractive index
have attracted attention due to their ability to unpair the relation
 between the shape of the optical lens with its optical response.
  For enhancing the versatility  of electrochemical gradients and its possible usage in
different kinds of devices and applications, it is
desirable to predesign GRIN structures with spatial
predictability of porosity and the corresponding etching rate.
In this work, we propose a simple model for the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous silicon structures with a controlled gradient in their
index of refraction. The characterization of some typical PS samples with
lateral porosity and thickness gradient (produced using pin Pt electrode)
with scanning electron microscopy and
ultraviolet-visible-near infrared reflectance spectroscopy was
found to be in conformity with the properties predicted through
the proposed model. In addition,
as the results allow us to obtain the complete dependence of
porosity, dielectric function and the corresponding etching rate for each
current density from some measurements performed on a single or
a couple of samples, the proposed model can facilitate the designing
of novel sensing devices based on surfaces with lateral gradient in refractive indices.}
Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

\section{Introduction}
\label{sec:introduction}
\notaV{
Introduction

Surfaces with gradient in the refractive index (GRIN) are of
importance not only due to the possibility of being able to
engineer/tune the propagation of light within the structure’s
surface for applications such as flat lenses, but also for several
interesting biological applications where the continual topographical
variation is being exploited \cite{pierscionek2012gradient}. As an example,
roughness dependent  response of the cells has been tested on such
materials for applications in medical implants \cite{bai2020bioinspired}.
 Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew.
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman,
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas.
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS
on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.
Among the electrochemical methods, compositional and doping density changes
in the conducting polymer have been used to produce the gradients using Indium tin
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach with an additional advantage of being compatible
with VLSI devices and integrable with microelectronics, for the fabrication
of refractive index (pore size) gradient has been the development of asymmetric
electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.

@@

%[Krueger, Neil A., et al.
% "Electrochemical Fabrication of Flat, Polymer‐Embedded
%Porous Silicon 1D Gradient Refractive Index Microlens
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].
Recently, J Wang et al. has shown the fabrication of
miniature spectrometer with PS based rugate filter using
radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna,
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to culture / adhesion of certain cells \cite{khung2008using}
In the investigation of such practically applicable systems,
the spacial predictability of electrochemical gradients can
be useful for predesigning the devices for different applications.
In this work, we report a simple analytical model to quantitatively
analyze the gradient (calculate the porosity /current density and
thickness) at any point of the GRIN structure.  The paper is organized
as follows. In Section 2  we report a simple analytical model to calculate
the current density/porosity and thickness  at any point of the GRIN structure.
The model contemplates (Dr. Mochan) the formation of electrochemically generated
porous surface  (applicable/extendible to photonic crystals with lateral gradient)
with lateral gradient in refractive index  ...with predictable  depth and porosity
at any point on surface.   In Section 3 we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section 4 includes experimental results and its comparison with numerically
evaluated parameters. Finally,  the conclusions are given in Section 5
%$
%
}

>>>>

\maketitle
\notaV{Index Structures (NOTE: WE NEED TO CHANGE THE NAME;
  Probably "Analytical model for  porous silicon structures with 1D
  gradient refractive index)}
\notaL{The calculation is 2D, seems 1D due to the narrow geometry chosen.}
\begin{abstract}

Layered systems with a lateral gradient in their refractive indices
and thicknesses may be employed for the development of a variety of
optical devices and
applications. They may be fabricated of porous silicon (PS) through a
position dependent electrochemical process. Thus, the possibility of
predicting the local current density $j$ and the co rresponding
porosity $p$
and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties with
ultraviolet-visible-near infrared reflectance
spectroscopy, \notaL{Should we mention microscopy?}, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves. We corroborated
our model by comparing the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel nonhomogenous devices with lateral gradients which can be used
for manifold applications.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}

\section{Introduction}
\label{sec:introduction}
Surfaces with gradient in the refractive index (GRIN) are of
importance not only due to the possibility of being able to
engineer/tune the propagation of light within the structure’s
surface for applications such as flat lenses, but also for several
interesting biological applications where the continual topographical
variation is being exploited \cite{pierscionek2012gradient}. As an example,
roughness dependent  response of the cells has been tested on such
materials for applications in medical implants \cite{bai2020bioinspired}.
 Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
%[W. F. Maier, K. Stçwe, S. Sieg, Angew.
%Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman,
%A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas.
%Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]
%%
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS
on gold electrode have been made by Shannon’s group\cite{wang2019fabrication}.
Among the electrochemical methods, compositional and doping density changes
in the conducting polymer have been used to produce the gradients using Indium tin
oxide electrode \cite{inagi2010bipolar}
%[S. Inagi, Y. Ishiguro et al Angew Chem Int. Ed. 2010, 49, 10136-10139;
%Angew Chem 2010 122, 10334-10337].
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of the polymers \cite{qin2020bipolar, ishiguro2011gradient}
%[Gradient Doping of Conducting Polymer
%Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami
%Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach with an additional advantage of being compatible
with VLSI devices and integrable with microelectronics, for the fabrication
of refractive index (pore size) gradient has been the development of asymmetric
electrode configuration in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.

@@

%[Krueger, Neil A., et al.
% "Electrochemical Fabrication of Flat, Polymer‐Embedded
%Porous Silicon 1D Gradient Refractive Index Microlens
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].
Recently, J Wang et al. has shown the fabrication of
miniature spectrometer with PS based rugate filter using
radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna,
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to culture / adhesion of certain cells \cite{khung2008using}
In the investigation of such practically applicable systems,
the spacial predictability of electrochemical gradients can
be useful for predesigning the devices for different applications.
In this work, we report a simple analytical model to quantitatively
analyze the gradient (calculate the porosity /current density and
thickness) at any point of the GRIN structure.  The paper is organized
as follows. In Section 2  we report a simple analytical model to calculate
the current density/porosity and thickness  at any point of the GRIN structure.
The model contemplates (Dr. Mochan) the formation of electrochemically generated
porous surface  (applicable/extendible to photonic crystals with lateral gradient)
with lateral gradient in refractive index  ...with predictable  depth and porosity
at any point on surface.   In Section 3 we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section 4 includes experimental results and its comparison with numerically
evaluated parameters. Finally,  the conclusions are given in Section 5
%$
%
